### 2019-12-29 defesa/tex/chapter/introducao.tex
wip

One of the 21 Karp's NP-Complete problems\footnote{The decision version, which asks if there is a cover of size $k$, is NP-Complete.} \cite{karp}, the Minimum Cover Problem is very well explored and considered to be a classic. 
Given a demand set along with a collection of subsets of the demand set, the problem is to determine the minimum number of elements from the collection of subsets that are needed to cover the whole demand set. One of its most famous examples is the Minimum Vertex Cover defined over graphs, where the vertex set has to be covered by a subset of edges.

>>>>

One of the 21 Karp's NP-Complete problems\footnote{The decision version, which asks if there is a cover of size $k$, is NP-Complete.} \cite{karp}, the Minimum Cover Problem is very well explored and considered to be a classic. 
Given a demand set along with a collection of subsets of the demand set, the problem is to determine the minimum number of elements from the collection of subsets needed to cover the whole demand set. One of its most famous examples is the Minimum Vertex Cover defined over graphs, where the vertex set has to be covered by a subset of edges.

### 2019-12-29 defesa/tex/chapter/pmclp.tex
wip

In this chapter, the classical version of PMCLP using disks will be defined and a version of the method will be proposed with the intention of later being used to solve the axis-parallel ellipses version of PMCLP. Throughout the course of this work, the maximal covering by disks problem is going to be referred to as $MCD(\Pp,m)$, where $\Pp$ is a set of points and $m$ is the number of unit disks.

\section{One disk, $MCD(\Pp,1)$}

Two exact methods for the $MCD(\Pp, 1)$ have been found in the literature. A $\bigO(n^2)$ algorithm is proposed by \cite{chazelle:1986} which improved the previously $\bigO(n^2\log{n})$ one proposed by \cite{drezner}.
As it has been mentioned, $MCD(\Pp,1)$ is a 3SUM-HARD problem, which means that it is as hard as the 3SUM problem (the problem of finding $3$ real numbers that sum to $0$, given $n$ real numbers). Initially the lower bound of the 3SUM problem was conjectured to be $\Omega(n^2)$, matching the best algorithm for $MCD(\Pp,1)$, which meant that no better time-complexity could be achieved. Since then, however, better algorithms for 3SUM have been developed with a $\bigO(\frac{n^2}{poly(n)})$ run time complexity \cite{3SUM-kopelowitz:2014}.

The $m=1$ version is treated here before the general case because it will be shown that, using the algorithm here proposed for $MCD(\Pp, 1)$, an optimal solution can be obtained for the $MCD(\Pp, m)$ as well as for the axis-parallel ellipse version of the problem.

>>>>

In this chapter, we introduce a version of the classical Euclidean norm PMCLP where the facilities have a radius-one coverage area. We refer to this problem as \sigla{MCD}{Maximum Covering by Disks}, as a radius-one coverage area in a Euclidean normed space is simply a unit disk. We also propose a method for it intending to adapt it for the elliptical PMCLP that will be introduced in the next chapter.

\section{Definition}

An instance of MCD is given by a set of $n$ demand points $\Pp:=\{p_1, \dots, p_n\}$, with $p_j\in\R^2$; and a set of $m$ disks $\D:=\{D_1, \dots, D_m\}$, which represents the facilities and are used to cover the demand set. Additionally, for every point in $\Pp$ a weight is given, and for every disk in $\D$ a coverage radius is given. The weight of the $j$-th point is denoted by $w_j\in\R_{>0}$, and the coverage radius of the $j$-th facility is denoted by $r_j \in \R_{>0}$.

A solution for an instance of MCD is determined by $Q:=(q_1, \dots, q_m) \in \R^{2m}$ which specifies the center of every disk in $\D$.
The coverage area of $j$-th disk centered at $q_j$ is denoted by $D_j(q_j)$. Finally, let $w : 2^{\Pp} \mapsto \R_{>0}$ be the function

\begin{equation}
w(A) = \sum_{j : p_j \in A} w_j,
\end{equation}
which takes a subset of $\Pp$ and returns the sum of the weights of every point in that subset, then an optimal solution of MCD is given by the optmization problem:

\begin{equation}
\max_{Q} w\left(\bigcup_{j=1}^m \Pp \cap D_j(q_j)\right).
\end{equation}

\subsection{CLS and CIPS}

The method proposed in \cite{church:1984} involves the creation of a \sigla{CLS}{Candidate List Set} which is a finite set of possible solutions that needs to be considered so the optimal solution is found.

\section{One unit disk version}

This is the case of MCD where $m=1$ and the only given disk has radius one. This version of the problem will be refered to as \sigla{MCD-1}{Maximum Covering by One Unit Disk}. Two exact methods for it have been found in the literature. A $\bigO(n^2)$ algorithm is proposed by \citeonline{chazelle:1986} which improved the previously $\bigO(n^2\log{n})$ one proposed by \citeonline{drezner}.
As it has been mentioned, MCD-1 is a 3SUM-HARD problem, which means that it is as hard as the 3SUM problem (the problem of finding $3$ real numbers that sum to $0$, given $n$ real numbers). Initially the lower bound of the 3SUM problem was conjectured to be $\Omega(n^2)$, matching the best algorithm for MCD-1, which meant that no better time-complexity could be achieved. Since then, however, better algorithms for 3SUM have been developed with a $\bigO(\frac{n^2}{poly(n)})$ run time complexity \cite{3SUM-kopelowitz:2014}.

This version is treated here before the general case because it will be shown that, using the algorithm here proposed for MCD-1, an optimal solution can be obtained for the MCD as well as for the axis-parallel ellipse version of the problem that will be introduced in the next chapter.
